---
title: "Pakistan GDP analysis"
author: "Khubaib"
date: "5/17/2020"
output:
  pdf_document: default
  html_document: default
---
First we freaking import the libraries or whatever it is called

```{r setup, include=FALSE}
library(tidyverse)
library(gapminder)
# Load the data
library(gapminder)
```

## One strange thing

I was seeing some of this dataset and found something *strange*. Let me show you
```{r}
bangladesh <- subset(gapminder,country=="Bangladesh")
ggplot(bangladesh,aes(x=year,y=pop)) + geom_point()
```

Do you see it? Bangladesh existed before 1970! That is clearly false. I think they seperated it. So time to bring it back to Pakistan to fix the analysis.

```{r}
Pakistan <- subset(gapminder,country == "Pakistan")
Pakistan <- Pakistan %>% mutate(actualGDP= gdpPercap * pop)
bangladesh<- bangladesh %>% mutate(actualGDP= gdpPercap * pop)
```

Now time to change the populations till 1971

```{r}
Pakistan[Pakistan$year<1972,"pop"] <-  Pakistan[Pakistan$year<1972,"pop"]+ bangladesh[bangladesh$year<1972,"pop"]
Pakistan[Pakistan$year<1972,"actualGDP"] <-  Pakistan[Pakistan$year<1972,"actualGDP"]+ bangladesh[bangladesh$year<1972,"actualGDP"]

```
Now the data looks a bit neat.
And how I want it

## Plotting GDP
Let's see the graph

```{r pressure, echo=FALSE}
ggplot(Pakistan,aes(x=year,y=actualGDP,color=gdpPercap)) + geom_line()
```
Now what we can see is that there was a major dip in GDP.
```{r}

ggplot(Pakistan,aes(x=year,y=actualGDP)) + geom_line() + lims(x=c(1967,1972),y=c(0,1.2e11))
```
That was due to war, hence War is bad. 
The end of a stupid petty analysis
Hopefully will lead to something better





